SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/papersincontext.tex
A bit of proofreading

Its main weakness is how it deals with authentication: The basic idea
is that when a client visits a resource, it will be told what
write operations it can perform. However, write operations will rarely
be permitted unless the client has authenticated and been authorised
to do so, and so, it assumes that credentials will be supplied with
the first read request. While the HTTP standard permits clients to
supply credentials with such requests, in practice, it rarely if ever
happens, possibly for privacy reasons. Thus, the server will have to
challenge the client first, but this should not happen on a resource
that the client is permitted to read. Therefore, the proposed hypermedia
needs a property so that the client understands what to do if it wants
to do write operations.

@@

Finally, the intention was to bring convergence in the topics of this
thesis around a system to cache results that could be reused in
subsequent queries. As noted in Section~\ref{sec:motivcache}, this was
motivated by opportunity as well as problems, but it is intended to
address
problems~\ref{prob:syntacticcache}~and~\ref{prob:cachecartesian}. This
work was not finished within the time frame of the dissertation, but
is discussed at length in Chapter~\ref{sec:tpfcacheplanning}. This
work relates to the problems in Section~\ref{sec:problems} as follows:
Triple Pattern Fragments shifts most of the processing from servers to
clients, but Problem~\ref{prob:microcontroller} makes that infeasible
in some cases.  In addition,
problems~\ref{prob:unknowndist},~\ref{prob:unknownconddist}~and~\ref{prob:largestats},
are compounded by Problem~\ref{prob:nostats}, but alleviated somewhat
by the presence of cardinality estimates given by Triple Pattern
Fragments, which we exploit.

>>>>

Its main weakness is how it deals with authentication: The basic idea
is that when a client visits a resource, it will be told what
write operations it can perform. However, write operations will rarely
be permitted unless the client has authenticated and been authorised
to do so, and so, it assumes that credentials will be supplied with
the first read request. While the HTTP standard permits clients to
supply credentials with such requests, in practice, it rarely if ever
happens, possibly for privacy reasons. Thus, the server will have to
challenge the client first, but this should not happen on a resource
that the client is permitted to read without authentication. 
Therefore, the proposed hypermedia needs a property so that the client
understands what to do if it wants to do write operations.

@@

Finally, the intention was to bring convergence in the topics of this
thesis around a system to cache results that could be reused in
subsequent queries. As noted in Section~\ref{sec:motivcache}, this was
motivated by opportunity as well as problems, but it is intended to
address
problems~\ref{prob:syntacticcache}~and~\ref{prob:cachecartesian}. This
work was not finished within the time frame of the dissertation, but
is discussed at length in Chapter~\ref{sec:tpfcacheplanning}. This
work further relates to the problems in Section~\ref{sec:problems} as follows:
Triple Pattern Fragments shifts most of the processing from servers to
clients, but Problem~\ref{prob:microcontroller} makes that infeasible
in some cases.  In addition,
problems~\ref{prob:unknowndist},~\ref{prob:unknownconddist}~and~\ref{prob:largestats},
are compounded by Problem~\ref{prob:nostats}, but alleviated somewhat
by the presence of cardinality estimates given by Triple Pattern
Fragments, which we exploit.

### 2016-07-25 dissertation/problems.tex
A bit of proofreading

As discussed in \ref{sec:prelimquery},

@@

To understand this, consider Example~\ref{ex:cartesian}, where the BGP
was a part of a query with 3 triple patterns. In addition to the two
triple patterns in Example~\ref{ex:cartesian}, a triple pattern that
connected the two, for example
\rdfterm{?person~foaf:publications~?paper~.}. If the result of this
triple pattern is cached, what is left to evaluate are the two triple
patterns in Example~\ref{ex:cartesian}, which is likely a very
expensive operation.

@@

He goes on to explain how linking such terms will help make
that inference, and how partial understanding is common in everyday
life and will also be sufficient in my cases on the Web. The practice
of using inference to find a common understanding is now known as
ontology matching or ontology alignment, and is a very active area of
research. This problem, as well as related problems, such as entity
resolution, are considered orthogonal to the problems in this thesis,
so the below problems are issues that arise from the ideal of an open
decentralised Web.

>>>>

As discussed in Section~\ref{sec:prelimquery},

@@

To understand this, consider Example~\ref{ex:cartesian}, and extend
the BGP to a query with 3 triple patterns. In addition to the two
triple patterns in Example~\ref{ex:cartesian}, add a triple pattern that
connect the two, for example
\rdfterm{?person~foaf:publications~?paper~.}. If the result of this
triple pattern is cached, what is left to evaluate are the two triple
patterns in Example~\ref{ex:cartesian}, which is likely a very
expensive operation.

@@

He goes on to explain how linking such terms will help make
that inference, and how partial understanding is common in everyday
life and will also be sufficient in my cases on the Web. The practice
of using inference to find a common understanding is now known as
ontology matching or ontology alignment, and is a very active area of
research. This problem, as well as related problems, such as entity
resolution, are considered orthogonal to the problems in this thesis,
so the below problems are issues that arise from the ideal of an open
decentralised Web. These problems are therefore not discussed further.
